---
title: "Speech emotion analysis: embarrasment features in Russian and French"
date: 10.06.2018
authors: Natalia Borisenko and Irina Nikishina
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show

---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Materials  
[Link to the data set](https://github.com/lilaspourpre/Linguistic-data-quantitative-analysis-and-visualisation/blob/master/project/dataset_embarr.csv) (csv file)  
[Link to audio](https://github.com/lilaspourpre/Linguistic-data-quantitative-analysis-and-visualisation/tree/master/project/audio)    
[Link to questionnaire](https://docs.google.com/forms/d/e/1FAIpQLSf6uuyYNl8ZlWfX3knrF-04q35faGCwP83PXebmEK59VTFQCA/viewform)  

## Introduction  
вЫсавк
### Describe the phenomenon.

### Provide information about the language (only for minor languages).
For the current task we use audios in Russian and French. These languages are among the six languages that are used in UN meetings.

### Mention some previous research (optional).
Embarrasment features in speech were previousely explored two years ago

## Research hypothesis  

As it has been already said we assume that mean embarrassment recognition value (hereinafter MERV) might depend on extra linguistic factors: gender, age, education and foreign language aquisition. As our null hypothesis we assume that none of the above mentioned factor do not affect MERV results.

Thus, in the current research we formulate the following null hypothesis:
1) MERV doesn't depend on gender:
*  MERV doesn't depend on gender for Russian audios
*  MERV doesn't depend on gender for French audios
*  MERV doesn't depend on gender for all audios

2) MERV doesn't depend on age
* MERV doesn't depend on age for Russian audios
* MERV doesn't depend on age for French audios
* MERV doesn't depend on age for all audios

3) MERV doesn't depend on education level
* MERV doesn't depend on education level for Russian audios
* MERV doesn't depend on education level for French audios
* MERV doesn't depend on education level for all audios

4) MERV doesn't depend on the English language aquisition
* MERV doesn't depend on the English language aquisition for Russian audios
* MERV doesn't depend on the English language aquisition for French audios
* MERV doesn't depend on the English language aquisition for all audios

5) MERV doesn't depend on the Frenchh language aquisition
* MERV doesn't depend on the Frenchh language aquisition for Russian audios
* MERV doesn't depend on the Frenchh language aquisition for French audios
* MERV doesn't depend on the Frenchh language aquisition for all audios

## Data  

Our dataset comprises 216 responces of 

```{r dataset}
df <- read.csv("example.csv")  
summary(df)
str(df)
```
* Our dependent variable is MERV -- mean embarrassement recognition value: average score for all audios 
* Predictor variables, their types, range/levels  

* Number of observations  

### Data collection and annotation   
Mention the source of your data, details of data collection. Justify the amount of data under study. In addition, you can discuss certain difficulties, peculiarities and shortcomings in data collection and annotation.  

### Data considerations
Discuss research design (if applicable), independence, autocorrelation, nestedness of data, possible biases, etc.


## R libraries in use
```{r libraries}
library(tidyverse)
# include R libraries here or later
```


## Analysis: descriptive statistics
In this section you can put tables and plots that show data distribution for individual variables and distribution for pairs of variables. Histograms, density plots, boxplots (or violin plots), mosaic plots are recommended. You can also provide some basic statistical analysis, such as correlation, statistical significance, t-test and other simple tests. If you calculate a chi-square statistic, do not forget to estimate the effect size.

## Multi-factor analysis  
At least two different methods have to be used. Please provide the output models summaries and graphs. Please evaluate your models (show and interpret relevant indicators such as classification accuracy, goodness of fit, classification power, inertia, variable significance, variable importance, etc.).   
It is recommended to report, when needed, how did you fit the model, did you find any signs of overfitting, why do you believe that certain model is an optimal one, etc.

## Linguistic interpretation of the quantitative results  

## Discussion on data distribution and quantitative methods in use   

In conclusion, you can suggest ideas for further development of your research (correction of hypotheses, work with the data, their statistical analysis).
